\documentclass[11pt,a4paper]{article}

\usepackage[margin=2.2cm]{geometry}
\usepackage{fancyhdr}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{caption}

\setlength{\headheight}{14pt}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Building a Minimal Command-Line Web Client in C}
\fancyhead[R]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

\titleformat{\section}{\Large\bfseries\color{blue!70!black}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\large\bfseries\color{blue!50!black}}{}{0em}{}

% Colors for progressive source listings
\definecolor{codeold}{gray}{0.58}
\definecolor{codebg}{RGB}{248,248,248}
\definecolor{newbg}{RGB}{232,245,233}
\definecolor{newframe}{RGB}{46,125,50}

\lstdefinestyle{basec}{
    language=C,
    basicstyle=\ttfamily\footnotesize,
    breaklines=true,
    breakatwhitespace=false,
    columns=fullflexible,
    keepspaces=true,
    numbers=left,
    numberstyle=\tiny\color{gray},
    numbersep=6pt,
    tabsize=4,
    showstringspaces=false,
    showspaces=false,
    captionpos=b,
    xleftmargin=1.2em,
    framexleftmargin=0.6em,
    aboveskip=0.4em,
    belowskip=0.15em
}

% Prior / unchanged code: light gray so it recedes
\lstdefinestyle{oldcode}{
    style=basec,
    basicstyle=\ttfamily\footnotesize\color{codeold},
    backgroundcolor=\color{codebg},
    keywordstyle=\color{codeold},
    commentstyle=\color{codeold},
    stringstyle=\color{codeold},
    identifierstyle=\color{codeold},
    frame=none,
    rulecolor=\color{gray!30}
}

% Newly added code: full color so it pops
\lstdefinestyle{newcode}{
    style=basec,
    basicstyle=\ttfamily\footnotesize\color{black},
    backgroundcolor=\color{newbg},
    keywordstyle=\color{blue!80!black},
    commentstyle=\color{green!45!black},
    stringstyle=\color{red!70!black},
    identifierstyle=\color{black},
    frame=leftline,
    framerule=2.5pt,
    rulecolor=\color{newframe}
}

% Standalone \"new code\" snippet (not part of full-file collage)
\lstdefinestyle{snippet}{
    style=basec,
    basicstyle=\ttfamily\footnotesize,
    backgroundcolor=\color{newbg},
    keywordstyle=\color{blue!80!black},
    commentstyle=\color{green!45!black},
    stringstyle=\color{red!70!black},
    frame=single,
    rulecolor=\color{newframe},
    aboveskip=0.8em,
    belowskip=0.8em
}

% Final complete file (everything \"new\" / current)
\lstdefinestyle{fullcode}{
    style=basec,
    basicstyle=\ttfamily\footnotesize,
    backgroundcolor=\color{gray!6},
    keywordstyle=\color{blue!80!black},
    commentstyle=\color{green!45!black},
    stringstyle=\color{red!70!black},
    frame=single,
    rulecolor=\color{gray!50},
    aboveskip=0.8em,
    belowskip=0.8em
}

% Continuous line numbers across old/new listing fragments of one file
% (Do not name these \end... --- LaTeX reserves that prefix for environments.)
\newcommand{\FullSourceStart}[1]{%
  \subsection{Full Source at This Stage}%
  \textit{Gray = already present. Green-highlighted = added in this step.}%
  \par\vspace{0.4em}%
  \lstset{name=#1}%
}
\newcommand{\FullSourceStop}{\lstset{name={}}}

\title{\textbf{Building a Minimal Command-Line Internet Client in C}\\[0.4em]
\large A Step-by-Step Tutorial}
\author{S.F.}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
This tutorial guides you through the creation of a compact yet powerful
command-line tool (\texttt{urlget}) capable of fetching web pages over HTTP
and HTTPS, with optional Tor support via SOCKS5. Development is incremental:
each step adds a focused piece of functionality, explains \emph{why} it exists,
and shows the complete source so far---with prior code muted in gray and new
code highlighted---so you always know what changed and where it lives.
\end{abstract}

\section*{Foreword}
\addcontentsline{toc}{section}{Foreword}

High-level libraries are wonderful until you need to know what they are
actually doing. This tutorial takes the opposite path: we talk to the network
with ordinary C, POSIX sockets, and a thin slice of OpenSSL. The point is not
machismo. It is demystification.

\textbf{Almost bare-metal networking is not hard.} Creating a socket,
connecting it, writing bytes, and reading bytes is a short, repeatable recipe.
Once those four moves are clear, you already understand the bulk of what every
network client does under the hood. Making the same path meaningfully faster
in user space usually means dropping to assembly (or accepting that the kernel,
the NIC, and physics own the rest of the budget). Clarity first; micro-optimizations
later, and only if measurement demands them.

\textbf{After the building blocks, the pattern barely changes.} Resolve an
address, open a socket, connect, send, receive, close. That loop is the same
whether the peer speaks HTTP, SMTP, a binary game protocol, or something you
invented this afternoon. What changes in the later stages is almost always the
\emph{payload}: is the protocol text or binary, how are messages framed, and
how do you parse them safely? HTTP headers, SOCKS5 handshakes, and TLS records
look different on the wire, but they all ride the same socket primitives.

\texttt{urlget} is a small vehicle for that idea---a mini command-line client
you can read end to end. If you finish it and think ``that was mostly sockets
plus parsing,'' the foreword did its job.

\hfill--- S.F.

\tableofcontents
\newpage

\include{step01_introduction}
\include{step02_skeleton}
\include{step03_usage}
\include{step04_arg_parsing}
\include{step05_url_parsing}
\include{step06_tcp_http}
\include{step07_https}
\include{step08_tor_socks5}
\include{step09_redirects}
\include{step10_advanced_features}
\include{step11_final_polish}

\end{document}
